Hyper-linked Communications: WebRTC enabled asynchronous collaboration

### 2016-03-13 tese1/XX_implementation_model.tex
[ADD] model, minor code refactoring

\begin{figure}[H]
    \centering
    \begin{subfigure}[b]{0.3\textwidth}
    	\includegraphics[width=\textwidth]{figures/model_data}
    \end{subfigure}
    \begin{subfigure}[b]{0.35\textwidth}
    	\includegraphics[width=\textwidth]{figures/model_data_permission}
    \end{subfigure}
    \caption{Generic data model}
\end{figure}

@@

Not less important, attributes can specify aggregations of objects. For example, the user role is an aggregator property that within users it allows the identifaction of each one is administrator. This aggregation specification is independent from the object type, so it's possible to search for the administrative role and return users and groups of users that contains that property.

Our model supports defining read and write permissions for each attribute, for example an attribute can be set to public read access or private write access to a set of entities. Implicitly if an entity can write an attribute it can also read it.

@@

\begin{figure}[H]
    \centering
    \begin{subfigure}[b]{0.25\textwidth}
    	\includegraphics[width=\textwidth]{figures/model_user}
    \end{subfigure}
    \caption{User model}
\end{figure}

@@

\begin{figure}[H]
    \centering
    \begin{subfigure}[b]{0.3\textwidth}
    	\includegraphics[width=\textwidth]{figures/model_relation}
    \end{subfigure}
    \caption{Relation model}
\end{figure}

A user can only interact with users that maintain a relationship with him or with users within the same group. In order to validate a relationship, both users must agree on that relationship, by other words it must exist a bi-directional relation between both users.

@@

A group can be public or private. If the group is public then it is visible to all users that mantain a relationship with a member of this group. If the group is private then it is only visible to their members.

\begin{figure}[H]
    \centering
    \begin{subfigure}[b]{0.3\textwidth}
    	\includegraphics[width=\textwidth]{figures/model_group}
    \end{subfigure}
    \begin{subfigure}[b]{0.3\textwidth}
    	\includegraphics[width=\textwidth]{figures/model_group_membership}
    \end{subfigure}
    \caption{Group model}
\end{figure}

@@

\begin{figure}[H]
    \centering
    \begin{subfigure}[b]{0.3\textwidth}
    	\includegraphics[width=\textwidth]{figures/model_message}
    \end{subfigure}
    \caption{Message model}
\end{figure}

@@

\begin{figure}[H]
    \centering
    \begin{subfigure}[b]{0.3\textwidth}
    	\includegraphics[width=\textwidth]{figures/model_hyper_content}
    \end{subfigure}
    \begin{subfigure}[b]{0.3\textwidth}
    	\includegraphics[width=\textwidth]{figures/model_time_tag}
    \end{subfigure}    
    \caption{Hyper content model}
\end{figure}

@@

\begin{figure}[H]
    \centering
    \begin{subfigure}[b]{0.3\textwidth}
    	\includegraphics[width=\textwidth]{figures/model_collaborative_content}
    \end{subfigure}
    \caption{Collaborative content model}
\end{figure}

@@

\begin{figure}[H]
    \centering
    \begin{subfigure}[b]{0.3\textwidth}
    	\includegraphics[width=\textwidth]{figures/model_recording_chunk}
    \end{subfigure}
    \begin{subfigure}[b]{0.3\textwidth}
    	\includegraphics[width=\textwidth]{figures/model_recording_interval}
    \end{subfigure}
    \caption{Recording model}
\end{figure}

>>>>

\begin{figure}[H]
    \centering
    \begin{subfigure}[b]{0.35\textwidth}
    	\includegraphics[width=\textwidth]{figures/model_data}
    \end{subfigure}
    \begin{subfigure}[b]{0.35\textwidth}
    	\includegraphics[width=\textwidth]{figures/model_data_permission}
    \end{subfigure}
    \caption{Generic data model}
\end{figure}

@@

% Not less important, attributes can specify aggregations of objects. For example, the user role is an aggregator property that within users it allows the identifaction of each one is administrator. This aggregation specification is independent from the object type, so it's possible to search for the administrative role and return users and groups of users that contains that property. <= [currently this operation is possible but it is not specified]

Not less important, our model supports defining read and write permissions for each attribute, for example an attribute can be set to public read access or private write access to a set of entities. Implicitly if an entity can write an attribute it can also read it.

The permission object is a mask of the data object, for each existing attribute in the data object it may exist the same attribute on the permission object specifying what entities can read or write it.

@@

\begin{figure}[H]
    \centering
    \begin{subfigure}[b]{0.20\textwidth}
    	\includegraphics[width=\textwidth]{figures/model_user}
    \end{subfigure}
    \caption{User model}
\end{figure}

@@

\begin{figure}[H]
    \centering
    \begin{subfigure}[b]{0.25\textwidth}
    	\includegraphics[width=\textwidth]{figures/model_relation}
    \end{subfigure}
    \caption{Relation model}
\end{figure}

A user can only interact with friends or with group members. In order to validate a friendship, both users must agree on that friendship, by other words it must exist a bi-directional relation between both users.

@@

A group can be public or private. If the group is public then it is visible to all users that mantain a friendship with a member of this group. If the group is private then it is only visible to their members.

\begin{figure}[H]
    \centering
    \begin{subfigure}[b]{0.30\textwidth}
    	\includegraphics[width=\textwidth]{figures/model_group}
    \end{subfigure}
    \begin{subfigure}[b]{0.25\textwidth}
    	\includegraphics[width=\textwidth]{figures/model_group_membership}
    \end{subfigure}
    \caption{Group model}
\end{figure}

@@

\begin{figure}[H]
    \centering
    \begin{subfigure}[b]{0.25\textwidth}
    	\includegraphics[width=\textwidth]{figures/model_message}
    \end{subfigure}
    \caption{Message model}
\end{figure}

@@

\begin{figure}[H]
    \centering
    \begin{subfigure}[b]{0.25\textwidth}
    	\includegraphics[width=\textwidth]{figures/model_hyper_content}
    \end{subfigure}
    \begin{subfigure}[b]{0.25\textwidth}
    	\includegraphics[width=\textwidth]{figures/model_time_tag}
    \end{subfigure}    
    \caption{Hyper content model}
\end{figure}

@@

\begin{figure}[H]
    \centering
    \begin{subfigure}[b]{0.25\textwidth}
    	\includegraphics[width=\textwidth]{figures/model_collaborative_content}
    \end{subfigure}
    \caption{Collaborative content model}
\end{figure}

@@

\begin{figure}[H]
    \centering
    \begin{subfigure}[b]{0.25\textwidth}
    	\includegraphics[width=\textwidth]{figures/model_recording_chunk}
    \end{subfigure}
    \begin{subfigure}[b]{0.25\textwidth}
    	\includegraphics[width=\textwidth]{figures/model_recording_interval}
    \end{subfigure}
    \caption{Recording model}
\end{figure}
